DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-01 paper/background.tex
..

\subsection{Deep End-to-End Learning in Autonomous Vehicles}

@@

The use of neural networks for end-to-end control of autonomous
driving was first demonstrated in late 1980s~\cite{Pomerleau1989},
using a small fully connected neural network; and subsequently in a
DARPA Autonomous Vehicle (DAVE) project in early
2000s~\cite{LeCun:04}, using a 6 layer convolutional neural network
(CNN); and most recently in NVIDIA's DAVE-2
project~\cite{Bojarski2016}, using 9 layer CNN. In all these projects,
the neural network models take raw image pixels as input and directly
produce steering control commands bypassing all intermediary steps and
hand-written rules in conventional robotics control approach. The
NVIDIA's latest effort reports that their trained CNN successfully
self-drive their modified cars in public roads without human
intervention~\cite{Bojarski2016}.

%% \cite{Levine2016}: ``In this paper, we aim to answer
%% the following question: does training the perception and control systems jointly end-toend
%% provide better performance than training each component separately?''

@@

\subsection{Embedded Multicore Single-Board-Computers}

Recent successes in AI, including NVIDIA's DAVE-2 showing, are due
in large part to the increased computing performance,
which afforded researchers to train and use ever deeper neural networks with
high accuracy. For practical, a computer platform in an automotive vehicle must
satisfy two often conflicting goals. One the one hand, the platform must provide
enough computing capacity for real-time processing of computationally expensive
AI workloads. On the other hand, the platform must also satisfy various
constrains such as cost, size, weight, and power consumption limits.
Because of these reasons, finding a right computing platform is non-trivial
task, one that requires deep understanding of the workloads and their
characteristics as well as the hardware platform that executes the
workloads. It is further complicated by the heterogeneity of available
computing hardware resources---multicore, GPU, DSP and other specialized
hardware accelerators.

>>>>

\subsection{End-to-End Deep Learning for Autonomous Vehicles}

@@

The use of neural networks for end-to-end control of autonomous
driving was first demonstrated in late 1980s~\cite{Pomerleau1989},
using a small fully connected neural network; and subsequently in a
DARPA Autonomous Vehicle (DAVE) project in early
2000s~\cite{LeCun:04}, using a 6 layer convolutional neural network
(CNN); and most recently in NVIDIA's DAVE-2
project~\cite{Bojarski2016}, using 9 layer CNN. In all these projects,
the neural network models take raw image pixels as input and directly
produce steering control commands bypassing all intermediary steps and
hand-written rules in conventional robotics control approach. The
NVIDIA's latest effort reports that their trained CNN successfully
self-drive their modified cars in public roads without human
intervention~\cite{Bojarski2016}. 
\fixme{Discuss the differences between Inferencing and
  Training. Real-time is most needed for inferencing operations.}

%% \cite{Levine2016}: ``In this paper, we aim to answer
%% the following question: does training the perception and control
%% systems jointly end-toend 
%% provide better performance than training each component separately?''

@@

\subsection{Embedded Computing Platforms for Real-Time Inferencing}

Recent successes in AI, including NVIDIA's DAVE-2 showing, are due
in large part to the increased computing performance,
which afforded researchers to train and use ever deeper neural networks with
high accuracy. For practical, a computer platform in an automotive vehicle must
satisfy two often conflicting goals. One the one hand, the platform must provide
enough computing capacity for real-time processing of computationally expensive
AI workloads. On the other hand, the platform must also satisfy various
constrains such as cost, size, weight, and power consumption limits.
Because of these reasons, finding a right computing platform is non-trivial
task, one that requires deep understanding of the workloads and their
characteristics as well as the hardware platform that executes the
workloads. It is further complicated by the heterogeneity of available
computing hardware resources---multicore, GPU, DSP, specialized
hardware accelerators, etc.
